Manuscript

### 2025-03-12 Manuscript_MD_ScoreReLiability.qmd
init rework results move tab_meanES combine tab_rel tab_tauES

As all phenomena in the collection fulfil the first condition, 50
phenomena have been catalogued where the effect is studied by comparing
the outcome across two separate groups. From the collection of 50
phenomena, 22 fulfil the second condition, so that estimates of score
reliability can be derived. For the 22 phenomena, the dependent variable
used to construct the effect size is measured by employing more than a
single indicator. At the same time, however, this implies that the
remaining 28 phenomena did not make use of more than a single indicator
to measure the dependent variable. Therefore, for the majority of
phenomena it is not possible to assess in how far measurement quality is
sufficiently high in terms of e.g. internal consistency or low random
error variance.

From the 22 phenomena that employed more than a single indicator, 19
made use of Likert-style items, where respondents would indicate their
agreement to some kind of statement. The scale-length varied from 3 to
10-points. The items measuring the remaining 3 phenomena were coded
dichotomously, as responses were right or wrong (2 cases), or expressed
agreement vs disagreement dichotomously (1 case). While the majority of
designs make use of some form of control-treatment manipulation,
randomly assigning participants to a condition (20 phenomena), some
phenomena refer to the effect of pre-existing differences, e.g.
biological sex (2 phenomena). Subsequently, those phenomena need to be
identified where the meta-analytic mean effect size is statistically
significant different from zero. This will be done as a first step of
this manuscript’s analysis procedure. Detailed information concerning
the different phenomena and how they were measured can be found at
\[osf-link\], while a brief summary can be found in Table 1.

@@

[Equations @eq-d], [-@eq-SEd], [-@eq-dc], and [-@eq-SEdc] were used to
generate estimates of standardized ES, both uncorrected and corrected,
with their corresponding standard errors. Generally, this leads to
larger (absolute) ES and larger standard errors. As an example from the
12 selected phenomena, the results from this procedure on Nosek’s
Explicit Art sex differences phenomenon are displayed in the forest plot
in Figure 1. Here, grey dots represent the uncorrected ES for each
sample, while black dots represent the corrected ES in each sample. The
bars surrounding these dots show the respective 95%-Cis.

@tbl-meanES demonstrates that what we observed in Figure 1 holds across
all 22 phenomena. All meta-analytic effect sizes are larger after
applying an attenuation correction procedure. Similarly, the uncertainty
quantified in the estimates’ standard error is larger. Additionally,
@tbl-meanES highlights which phenomena pass criterion (3) – the effect
size must be statistically significantly distinguishable from zero. 12
phenomena pass this criterion, highlighted in boldface. It may be
remarked that the attenuation correction procedure, in this data,
appears to have no influence on whether a phenomenon passes the
criterion. The differences in p-value are rather small and lead to no
difference in conclusion, regarding a significance level of .05.

```{r, echo = FALSE}
#| label: tbl-tauES
#| tbl-cap: Tests for ES Heterogeneity
knitr::kable(x = read.csv(here("Tables/Heterogeneity_ES.csv")))
```

>>>>

As all phenomena in the collection fulfil the first condition, 50
phenomena have been catalogued where the effect is studied by comparing
the outcome across two separate groups. From the collection of 50
phenomena, 21 fulfil the second condition, so that estimates of score
reliability can be derived. For the 21 phenomena, the dependent variable
used to construct the effect size is measured by employing more than a
single indicator. At the same time, however, this implies that the
remaining 29 phenomena did not make use of more than a single indicator
to measure the dependent variable. Therefore, for the majority of
phenomena it is not possible to assess in how far measurement quality is
sufficiently high in terms of e.g. internal consistency or low random
error variance.

From the 21 phenomena that employed more than a single indicator, 19
made use of Likert-style items, where respondents would indicate their
agreement to some kind of statement. The scale-length varied from 3 to
10-points. The items measuring the remaining 2 phenomena were coded
dichotomously, as responses were right or wrong. While the majority of
designs make use of some form of control-treatment manipulation,
randomly assigning participants to a condition (20 phenomena), some
phenomena refer to the effect of pre-existing differences, e.g.
biological sex (2 phenomena). Subsequently, those phenomena need to be
identified where the meta-analytic mean effect size is statistically
significant different from zero. This will be done as a preliminary step in
this manuscript’s analysis procedure. Detailed information concerning
the different phenomena and how they were measured can be found at
\[osf-link\], while a brief summary can be found in Table 1.

[Equations @eq-d], [-@eq-SEd], [-@eq-dc], and [-@eq-SEdc] were used to
generate estimates of standardized ES, both uncorrected and corrected,
with their corresponding standard errors. Generally, this leads to
larger (absolute) ES and larger standard errors. As an example from the
21 selected phenomena, the results from this procedure on Nosek’s
Explicit Art sex differences phenomenon are displayed in the forest plot
in @fig-forest. Here, grey dots represent the uncorrected ES for each
sample, while black dots represent the corrected ES in each sample. The
bars surrounding these dots show the respective 95%-Cis.

@tbl-meanES demonstrates that what we observed in Figure 1 holds across
all 21 phenomena. All meta-analytic effects are larger in their absolute size after
applying an attenuation correction procedure. Similarly, the uncertainty
quantified in the estimates’ standard error is larger. Additionally,
@tbl-meanES highlights which phenomena pass criterion (3) – the effect
size must be statistically significantly distinguishable from zero. 12
phenomena pass this criterion, highlighted in boldface. It may be
remarked that the attenuation correction procedure, in this data,
appears to have no influence on whether a phenomenon passes the
criterion. The differences in p-value are rather small and lead to no
difference in conclusion, regarding a significance level of .05.

@@

```{r, echo = FALSE}
#| label: tbl-tauES
#| tbl-cap: Tests for ES Heterogeneity
#knitr::kable(x = read.csv(here("Tables/Heterogeneity_ES.csv")))

tab_hetES <- read.csv(here("Tables/Heterogeneity_ES.csv"))
tab_hetrel <- read.csv(here("Tables/Results_RMA_alpha.csv"))

tab_both <- data.frame(tab_hetES$MASC,
                       tab_hetrel[,c("mu_alpha_str", "tau_alpha", "QE_str", "QEp")],
                       tab_hetES[,c("tau_raw", "QE_raw_str", "QEp_raw", "tau_cor", "QE_cor_str", "QEp_cor")])

knitr::kable(tab_both)
```
